### 2022-08-29 README.Rmd
update matrix

<!-- badges: start -->
[![R build status](https://github.com/cboettig/neonstore/workflows/R-CMD-check/badge.svg)](https://github.com/cboettig/neonstore/actions)
[![Codecov test coverage](https://codecov.io/gh/cboettig/neonstore/branch/master/graph/badge.svg)](https://codecov.io/gh/cboettig/neonstore?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/neonstore)](https://CRAN.R-project.org/package=neonstore)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![R build status](https://github.com/cboettig/neonstore/workflows/R-CMD-check/badge.svg)](https://github.com/cboettig/neonstore/actions)
[![Codecov test coverage](https://codecov.io/gh/cboettig/neonstore/branch/master/graph/badge.svg)](https://app.codecov.io/gh/cboettig/neonstore?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/neonstore)](https://CRAN.R-project.org/package=neonstore)
[![R-CMD-check](https://github.com/cboettig/neonstore/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/cboettig/neonstore/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->
